---
title: "Homework 6"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(rvest)
library(ggplot2)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)


theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colur = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

Hello! And welcome to my solutions for Homework 6. Enjoy.

## Problem 1

Read in the data. 

```{r}
homicide_df = 
  read_csv("./data/homicide_data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1
    )
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa_AL",
    city_state != "Tulsa, AL"
    ) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex) %>% 
  view

```

Start with one city

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df, 
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results)%>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))

```

```{r}
model_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR))+
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2 

Firstly, let's read in the data and fit a model that may explain birthweight. 

```{r, Example of finding residuals}
baby_df = read_csv("./data/birthweight_data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex), 
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )

model_1 = lm(bwt ~ momage * delwt, data = baby_df)

baby_df %>% 
  add_predictions(model_1) %>%
  add_residuals(model_1) %>% 
  ggplot(aes(x = resid, y = pred))+
  geom_point()+
  labs(title = "Plot of model residuals against fitted values")

```

Now, let's compare this first model to two other models and see which one has the smallest RSME. 

```{r}

model_2 = lm(bwt ~ gaweeks, data = baby_df)
model_3 = lm(bwt ~ bhead * blength * babysex, data = baby_df)

cv_df = crossv_mc(baby_df, 100)

cv_df = 
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )


cv_df = 
  cv_df %>% 
  mutate(
    model_1 = map(.x = train, ~lm(bwt ~ momage * delwt, data = .x)),
    model_2 = map(.x = train, ~lm(bwt ~ gaweeks, data = .x)),
    model_3 = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = model_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(), 
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse))+
  geom_violin()

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(), 
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rsme = mean(rmse))
```

Model 3 does the best at explaining the relationship.  



## Problem 3 


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_model = lm(tmax ~ tmin, data = weather_df) 

weather_results = 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    r_squared = map(models, broom::glance),
    logs = map(models, broom::tidy)
  ) %>% 
  unnest(r_squared) %>% 
  select(strap_number, r.squared, logs) %>% 
  unnest(logs) %>% 
  select(strap_number, r.squared, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  rename(
    beta_0 = "(Intercept)",
    beta_1 = "tmin"
  ) %>% 
  mutate(
    log_b0_b1 = log((beta_0 * beta_1))
  ) %>% 
  select(r.squared, log_b0_b1)
```

Let's plot the data. 

```{r}

weather_results %>% 
  ggplot(aes(x = r.squared))+
  geom_density()

weather_results %>% 
  ggplot(aes(x = log_b0_b1))+
  geom_density()

```

These two plots are seemingly standard bell curve. The r squared estimate is slightly left skewed. 


Let's identify the confidence intervals for these estimates 

```{r}
ci_r = 
  weather_results %>%
  pull(r.squared) %>% 
  quantile( c(0.025, 0.975)) %>% 
  knitr::kable( caption = "95% Confidence Interval for R Squared Estimate")

ci_r

ci_logs = 
  weather_results %>%
  pull(log_b0_b1) %>% 
  quantile( c(0.025, 0.975))%>% 
  knitr::kable( caption = "95% Confidence Interval for log(β̂0∗β̂) Estimate")

ci_logs

```

